---
title: "Starbucks Analysis"
author: "Deepak Kumar"
date: "July 20, 2017"
output: 
      html_document:
      fig_width: 10
      fig_height: 5
      toc : yes
      number_sections: yes
      code_folding: show 
      
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading data into the dataframe,

```{r}
setwd("C:/Users/Deepak kumar/Downloads/R/Starbucks Analysis")
getwd()
library(plotly)
library(tidyr)
library(ggplot2)
library(formattable)
library(DT)
library(lattice)
library(maps)
library(ggmap)
library(tidyverse)
star=read.csv("directory.csv",stringsAsFactors = FALSE,header=TRUE)
```

#Data Cleaning and Analysis:
Let us analyse the data given and try to gather some intersting insights.

```{r}
glimpse(star)
dim(star)
```

> Brand:

The brand column contains 4 values - 

* Starbucks- American Coffee House
* Evolution Fresh - Subsidary of Starbucks .They are into cold pressed jiice and Smoothies.
* Teavana - Acquired by Starbucks and carter to Loose leaf tea.
* Coffee House Holding - Subsiary of Starbucks.

## Let us now analyse each of the compaies presense country,city and statewise.

```{r}
temp=filter(star[star$Brand=="Coffee House Holdings",])
dim(temp)
datatable(temp)
```

It is seen that Starbucks operates Coffee House Holdings at one location -Seattle,US.

```{r}
temp=filter(star[star$Brand=="Teavana",])
dim(temp)
temp=temp %>% group_by(Country) %>% summarise(count=n())
q=ggplot(temp,aes(x=factor(Country,levels=Country),y=count,fill=Country))+geom_bar(stat="identity")+theme(axis.title.x = element_text(angle=90))+labs(x="Country",y="Count")+ggtitle("Teavana Stores by Country")
ggplotly(q)
```

##Evolution Fresh Stores:

```{r}
temp=filter(star[star$Brand=="Evolution Fresh",])
dim(temp)
datatable(temp)
```
Evolution fresh stores are located at 2 places in Seattle .Lets focus on Starbucks now.

##Starbucks

```{r}
temp=filter(star[star$Brand=="Starbucks",])
dim(temp)
temp=na.omit(temp)
count=temp %>% group_by(Country) %>% summarise(count=n(),percentage=(count/dim(temp)[1]) * 100) %>% arrange(desc(count))
datatable(count)
stat=temp %>% group_by(State.Province) %>% summarise(count=n(),percentage=(count/dim(temp)[1])*100) %>% arrange(desc(count))
datatable(count)
cit=temp %>% group_by(City) %>% summarise(count=n(),percentage=(count/dim(temp)[1])*100) %>% arrange(desc(count))
datatable(cit)
plot_ly(count,x=~count,y=~percentage,color=count$Country,mode="markers",name="Percentage wise store distribution",text=paste('Country:',count$Country)) %>% layout(title="Percentage wise store distribution",showlegend= FALSE)
plot_ly(stat,x=~count,y=~percentage,color=stat$State.Province,mode="markers",name="Percentage wise store distribution",text=paste('State:',stat$State.Province))%>% layout(title="Percentage wise store distribution",showlegend= FALSE)
plot_ly(cit,x=~count,y=~percentage,color=cit$City,type="scatter",mode="marker",name="Percentage wise store distribution",text=paste('City:',cit$City)) %>% layout(title="Percentage wise store distribution",showlegend= FALSE)
```


##Let us now analyse the type of ownership

```{r}
own=temp %>% group_by(Ownership.Type) %>% summarise(count=n(),percentage=(count/dim(temp)[1])*100)
q=ggplot(own,aes(x=count,y=percentage,color=Ownership.Type))+geom_point()+ggtitle("Ownership Type")
ggplotly(q)
```


#Indian Operations of Starbucks:

```{r}
Ind=filter(star[star$Country=="IN",])
datatable(Ind)
```

The Indian Operation is an JV between Starbucks and TATA.


Work in progress....